---
title: "UFO Report"
output: html_document
---

```{r library, include=FALSE, echo=FALSE}
df <- read.csv("data/UFOCoords.csv")
library(dplyr)
library(knitr)
library(ggplot2)
knitr::opts_chunk$set(error=TRUE)
```

```{r summary, echo=FALSE}
source("scripts/summary.R")
```

## Summary
This is a report of UFO sighting in the United States and Canada. This report draws upon data from the [data.world](https://data.world/timothyrenner/ufo-sightings). As an overview, here is a summary of the key variables from the data.

- Total appearances of UFO (2016): `r summary$length`
- Most appeared time period: `r summary$time_day`
- Most appeared time: `r summary$common_time`
- Most appeared area: `r summary$most_occurances`
- Most appeared shape: `r summary$common_shape`

## UFO appearances in North America

```{r plots1, message=FALSE, echo=FALSE}
source("scripts/Chart_1.R")
plot_1(df)
```

## UFO Shapes Spotted in the United States

```{r plot2, message=FALSE, echo=FALSE}
source("scripts/Chart_2.R")
plot_2(df)
```